### 2024-12-07 skripsi/chapter2.tex
finish ch4 computational model, start implementation

After eliminating $W$ and $\vb*{e}$, with $\vb{1}_{n} = \langle 1,\dots,1\rangle$, $\vb{y} = \lbrack y_1, \dots, y_n \rbrack $, and ${\alpha} = \lbrack \alpha_1, \dots, \alpha_n \rbrack $ the solution is as follows in block matrix notation
\begin{equation} \label{eq:lssvrSolution}
  \begin{bmatrix}
    0          & \vb{1}_{n}^{\intercal} \\
    \vb{1}_{n} & \Omega + \frac{I}{C}
  \end{bmatrix}
  \begin{bmatrix}
    b           \\
    \vb{\alpha} \\
  \end{bmatrix}
  =
  \begin{bmatrix}
    0      \\
    \vb{y} \\
  \end{bmatrix}
\end{equation}

The solution in \cref{eq:lssvrSolution}

\begin{algorithm}[H]
  \caption{LSSVR Training}\label{alg1:cap}
  \begin{algorithmic}[1]
    \Require $\vb{X}, \vb{y}, \gamma$
    \Ensure $\vb{\alpha}, b$
    \State $\Omega \gets [[]]$ \Comment{Construct matrix of inner products in high dimensional space}

    \For{$k=0 \to n$}
    \For{$l=0 \to n$}
    \State$\Omega_{k,l}\gets K(\vb{X}_k,\vb{X}_l)$
    \EndFor
    \EndFor
    \State $\vb{H} \gets \Omega + \frac{\vb{I}}{\gamma}$
    % \State $\vb{1} \gets [1,1,...,1]$
    \State $\vb{A} \gets [[]]$ \Comment{Construct left hand side matrix}
    \State $\vb{A}_{0,0} \gets 0$
    \For{$k=0 \to n$}
    \State $\vb{A}_{k+1,0} \gets 1$
    \State $\vb{A}_{0,k+1} \gets 1$
    \EndFor
    \For{$k=0 \to n$}
    \For{$l=0 \to n$}
    \State $\vb{A}_{k+1,l+1} \gets \vb{H}_{k,l}$
    \EndFor
    \EndFor
    \State $\vb{B}\gets []$ \Comment{Construct left hand side of the equation}
    \State $\vb{B}_0 \gets 0$
    \For{$k=0 \to n$}
    \State $\vb{B}_{k+1} \gets \vb{y}_{k}$
    \EndFor
    \State $\vb{A}^{\dagger} \gets pseudoInverse(\vb{A})$ \Comment{Compute solution using pseudo inverse}
    \State $\vb{S} \gets \vb{A}^{\dagger}\vb{B}$
    \State $b \gets \vb{S}_{0}$
    \For{$k=0 \to n$}
    \State $\vb{\alpha}_{k} \gets \vb{S}_{k+1}$
    \EndFor
  \end{algorithmic}
\end{algorithm}

The basic psuedocode from the LSSVM Equation for function regression is defined in \nameref{alg1:cap} for a training set of length $n$, features $\vb{X}$, and labels $\vb{y}$. Training the LSSVM means computing the values of langrange multipliers $\vb{\alpha}$ and bias $b$. $K$ is the kernel function used to compute the inner products in high dimensional space, here we asume the RBF kernel. $\vb{A}$ is a matrix of size $n+1$ by $n+1$. $\vb{H}$ is a matrix of size $n$ by $n$. $\vb{I}$ is the identity. $\vb{B}$ is a vector of size $n+1$. $\vb{S}$ is a vector of size $n+1$.

After training the model can be used for prediction of unseen points. The psuedocode for prediction is shown in \nameref{alg2:cap} for prediction features $\vb{U}$. The trained model uses the learned multipliers of training points $\vb{\alpha}$, the training points themselves $\vb{X}$, and the bias $b$.

\begin{algorithm}[H]
  \caption{LSSVR Prediction}\label{alg2:cap}
  \begin{algorithmic}[1]
    \Require $\vb{U}, \vb{\alpha}, \vb{X}, b$
    \Ensure $\vb{v}$
    \State $\Omega \gets [[]]$ \Comment{Construct matrix of inner products in high dimensional space}

    \For{$k=0 \to m$}
    \For{$l=0 \to n$}
    \State$\Omega_{k,l}\gets K(\vb{U}_{k},\vb{X}_l)$
    \EndFor
    \EndFor
    \State $\vb{v} \gets \Omega\vb{\alpha} + \vb{1}_{m}b$
  \end{algorithmic}
\end{algorithm}

>>>>

After eliminating $W$ and $\vb*{e}$, with $\vb{1}_{n} = \langle 1,\dots,1\rangle$, $\vb{y} = \lbrack y_1, \dots, y_n \rbrack $, and ${\alpha} = \lbrack \alpha_1, \dots, \alpha_n \rbrack $ the solution is as follows in block matrix notation
\begin{equation} \label{eq:lssvr_solution}
  \begin{bmatrix}
    0          & \vb{1}_{n}^{\intercal} \\
    \vb{1}_{n} & \Omega + \frac{I}{C}
  \end{bmatrix}
  \begin{bmatrix}
    b           \\
    \vb{\alpha} \\
  \end{bmatrix}
  =
  \begin{bmatrix}
    0      \\
    \vb{y} \\
  \end{bmatrix}
\end{equation}

The solution in \cref{eq:lssvr_solution}

\begin{algorithm}[H]
  \caption{LSSVR Training}\label{alg:lssvr_training}
  \begin{algorithmic}[1]
    \Procedure{SolveLSSVR}{$\vb{X}, \vb{y}, \gamma $}
    \State{\(\Omega \gets [[]]\)}
    \Comment{Construct matrix of inner products in high dimensional space}

    \For{\(k=0 \to n\)}
    \For{\(l=0 \to n\)}
    \State{\(\Omega_{k,l}\gets K(\vb{X}_k,\vb{X}_l)\)}
    \EndFor{}
    \EndFor{}
    \State{\(\vb{H} \gets \Omega + \frac{\vb{I}}{\gamma}\)}
    % \State $\vb{1} \gets [1,1,...,1]$
    \State{\(\vb{A} \gets [[]]\)}
    \Comment{Construct left-hand side matrix}
    \State{\(\vb{A}_{0,0} \gets 0\)}
    \For{\(k=0 \to n\)}
    \State{\(\vb{A}_{k+1,0} \gets 1\)}
    \State{\(\vb{A}_{0,k+1} \gets 1\)}
    \EndFor{}
    \For{\(k=0 \to n\)}
    \For{\(l=0 \to n\)}
    \State{\(\vb{A}_{k+1,l+1} \gets \vb{H}_{k,l}\)}
    \EndFor{}
    \EndFor{}
    \State{\(\vb{B}\gets []\)}
    \Comment{Construct left-hand side of the equation}
    \State{\(\vb{B}_0 \gets 0\)}
    \For{\(k=0 \to n\)}
    \State{\(\vb{B}_{k+1} \gets \vb{y}_{k}\)}
    \EndFor{}
    \State{\(\vb{A}^{\dagger} \gets pseudoInverse(\vb{A})\)}
    \Comment{Compute solution using pseudo inverse}
    \State{\(\vb{S} \gets \vb{A}^{\dagger}\vb{B}\)}
    \State{\(b \gets \vb{S}_{0}\)}
    \For{\(k=0 \to n\)}
    \State{\(\vb{\alpha}_{k} \gets \vb{S}_{k+1}\)}
    \EndFor{}
    \State{\textbf{return}\(\vb{\alpha}, b\)}
    \EndProcedure{}
  \end{algorithmic}
\end{algorithm}

The basic pseudocode from the LSSVM Equation for function regression is defined in \lccref{alg:lssvr_training} for a training set of length $n$, features $\vb{X}$, and labels $\vb{y}$. Training the LSSVM means computing the values of langrange multipliers $\vb{\alpha}$ and bias $b$. $K$ is the kernel function used to compute the inner products in high dimensional space, here we assume the RBF kernel. $\vb{A}$ is a matrix of size $n+1$ by $n+1$. $\vb{H}$ is a matrix of size $n$ by $n$. $\vb{I}$ is the identity. $\vb{B}$ is a vector of size $n+1$. $\vb{S}$ is a vector of size $n+1$.

After training the model can be used for prediction of unseen features. The pseudocode for prediction is shown in \lccref{alg:lssvr_prediction} for prediction features $\vb{U}$ with \(p \) samples. The trained model uses the training features themselves $\vb{X}$ with \(n \) samples, the learned multipliers of training points $\vb{\alpha}$, and the bias $b$.

\begin{algorithm}[H]
  \caption{LSSVR Prediction}\label{alg:lssvr_prediction}
  \begin{algorithmic}[1]
    \Require $\vb{U}, \vb{\alpha}, \vb{X}, b$
    \Ensure $\vb{v}$
    \State $\Omega \gets [[]]$ \Comment{Construct matrix of inner products in high dimensional space}

    \For{$k=0 \to p$}
    \For{$l=0 \to n$}
    \State$\Omega_{k,l}\gets K(\vb{U}_{k},\vb{X}_l)$
    \EndFor
    \EndFor
    \State $\vb{v} \gets \Omega\vb{\alpha} + \vb{1}_{m}b$
  \end{algorithmic}
\end{algorithm}

### 2024-12-07 skripsi/chapter4.tex
finish ch4 computational model, start implementation

\section{Data Retrieval}
\noindent The second data acquisition approach retrieves data of a from an external source. This approach downloads the external data to a local machine. In this study, the specific dataset that will be used is the ERA5 dataset from the European Center for Medium-range Weather Forecast (ECMWF). Specifically, the ERA5 dataset is a reanalysis which means it combines observational data from all over the world in order to present a more complete picture of the weather system. This combination process, named 4D variational data assimilation, takes into account the physics known to be involved in the system. As an example weather station data which take measurements such as wind speed, humidity, and temperature of the immediate surroundings of the weather station is very limited in giving a broader picture of weather over a larger area. Even technologies like earth observations satellites are limited to what they can observe at any single point in time as most cannot see the entirety of the earth's surface at once. The ERA5 dataset specifically, assimilates previous forecasts with observational data every 12 hours. The ERA5 reanalysis is available at the following url (\url{https://cds.climate.copernicus.eu/datasets/reanalysis-era5-single-levels}).

@@

\section{Design of Computational Model}
\noindent In this section, we will discuss the design of the computational model that is proposed in this work. An illustration of the computational model is show in \lccref{fig:computational_model}.

@@

The computational is divided into four large phases. The processes within these phases are based on the broad outcomes of the phase. The phases themselves are data preparation, data transformation, model training, and model evaluation. Each phase is composed of processes that together works toward the output of the larger process.

@@

The second type of dataset is retrieved from an external source. The data source is first identified, in our case it is the WeatherBench 2 collection of datasets. The specific dataset from the collection of different dataset versions is first determined. And then, we determine the filters for the portions of the dataset we are interested in. Once the dataset and filters are determined, the retrieval process starts by accessing the dataset using the \emph{Xarray} library \autocite{hoyer2017xarray,hoyerXarray2024}. The filters are applied as in . % TODO: add figure for filtering process and local save process
The filtered version is then stored locally. Using the stored dataset, the basis coefficients of the data is computed using a discrete Fourier transform.

@@

\subsection{Model Training}

\subsection{Model Evaluation}

\section{Implementation of Computational Model}
\noindent

>>>>

\section{Data Retrieval}\label{sec:data_retrieval}
\noindent The second data acquisition approach retrieves data of a from an external source. This approach downloads the external data to a local machine. In this study, the specific dataset that will be used is the ERA5 dataset from the European Center for Medium-range Weather Forecast (ECMWF). Specifically, the ERA5 dataset is a reanalysis which means it combines observational data from all over the world in order to present a more complete picture of the weather system. This combination process, named 4D variational data assimilation, takes into account the physics known to be involved in the system. As an example weather station data which take measurements such as wind speed, humidity, and temperature of the immediate surroundings of the weather station is very limited in giving a broader picture of weather over a larger area. Even technologies like earth observations satellites are limited to what they can observe at any single point in time as most cannot see the entirety of the earth's surface at once. The ERA5 dataset specifically, assimilates previous forecasts with observational data every 12 hours. The ERA5 reanalysis is available at the following url (\url{https://cds.climate.copernicus.eu/datasets/reanalysis-era5-single-levels}).

@@

\section{Design of Computational Model}\label{sec:computational_model_design}
\noindent In this section, we will discuss the design of the computational model that is proposed in this work. An illustration of the computational model is show in \lccref{fig:computational_model}.

@@

The computational model is divided into four large phases. The processes within these phases are based on the broad outcomes of the phase. The phases themselves are data preparation, data transformation, model training, and model evaluation. Each phase is composed of processes that together works toward the output of the larger process.

@@

The second type of dataset is retrieved from an external source. The data source is first identified, in our case it is the WeatherBench 2 collection of datasets. The specific dataset from the collection of different dataset versions is first determined. The dataset is available in the \emph{Zarr} format. And then, we determine the filters for the portions of the dataset we are interested in. Once the dataset and filters are determined, the retrieval process starts by accessing the dataset using the \emph{Xarray} library \autocite{hoyer2017xarray,hoyerXarray2024}. The filters are applied as in .... % TODO: add figure for code of the filtering process and local save process
Finally, the filtered version is stored locally. The local dataset is also stored in the \emph{Zarr} format.

@@

\noindent The second phase of the computational model transforms the data that has been prepared into a form that can be used with the proposed model. In this study, there are two ways a dataset can be used. The first and simplest way is to predict the solution function from the forcing term for a given set of PDE parameters. In this case, the input function is the forcing term. In other words, the input function is the predictor or independent variable that will be used to predict the solution function. As such, the output function is the solution function. The antiderivative dataset is used in this way. The derivative, which represents the acceleration function, is used to predict the velocity function. Which means that the input function is the acceleration function and the output function is the velocity function. The second use of a dataset depends on whether it can be interpreted as a mapping of a previous function to the next function. In other words, a series of functions related to the previous function as a sum of the previous function and a perturbation. A commonly used form of this are time series. Generally, a time series can be represented as \lccref{eq:time_step_function}. This function describes the evolution of function \(f\) as a sum of some initial state \(f^0\) and perturbation which is its rate of change \(\dv{f}{t}\) at a point in time close to the current time multiplied by the time step \(\delta t\).
\begin{equation}
  f^{t+1} = f^{t} + \delta t \times \dv{f}{t} \label{eq:time_step_function}
\end{equation}
In this case the previous function and any other independent variables like the forcing term involved in the time derivative \(\dv{f}{t}\) is used to predict the perturbation which is the time derivative itself. It would mean that each sample function in the data would need to at least have two dimensions. This is because one dimension represents the evolution of the function over time, while the other dimensions define the spatial domain where the function's values are computed at each time step. This condition is true for both the Burgers' equation dataset and the WeatherBench 2 collection of ERA5 datasets. First, the Burgers' equation dataset, while is also able to be used in the first way as a mapping between the forcing term and the solution, one of the traditional ways of solving it is using the method of lines in conjunction with another method such as the finite differences method or the spectral method. In both of these, the Burgers' equation is formulated as an initial value problem, using the finite differences to computing the time derivative. % TODO: add figures and citation for this, or if this is avaliable in a different place in the thesis a refference to that.
The method of lines approach in one of its forms is equal to \lccref{eq:time_step_function} \autocite{schiesserNumericalMethodLines2012,sadikuSimpleIntroductionMethod2000}. As such the Burgers' equation dataset can also be used in this way. In this case, algebraic manipulation of \lccref{eq:forced_viscous_burgers} results in the time derivative of the solution as in \lccref{eq:forced_viscous_burgers_time_derivative}.
\begin{align}
  \pdv{u}{t} = f - u\pdv{u}{x} + \nu\pdv[2]{u}{x} \label{eq:forced_viscous_burgers_time_derivative}
\end{align}
As can be seen, the time derivative is expressed in terms of the solution function, the forcing term and any other partial derivatives. Because of this, it means we can train the model to learn the relationship between the solution function combined with the forcing term and the time derivative. Putting this together with \lccref{eq:time_step_function}, it is possible to predict the solution function in a future time based on the current solution function and forcing term. The input functions in this case are both the value of the solution function and the forcing term at the current time step. The output function is the time derivative which is computed by rearranging \lccref{eq:time_step_function} resulting in \lccref{eq:time_derivative_time_step_function}.
\begin{equation}
  \dv{f}{t} = \frac{f^{t+1} - f^{t}}{\delta t} \label{eq:time_derivative_time_step_function}
\end{equation}
Perhaps in a more obvious manner, the same is also applied to the WeatherBench 2 collection of ERA5 datasets. The 2-meter temperature is a series of snapshots in time of the distribution of temperature all over the world at 2 meters above the surface. The input function in this case is the temperature distribution at the current time step. The output function is the time derivative of the temperature distribution computed using \lccref{eq:time_derivative_time_step_function}.

The input and output functions are then transformed into basis coefficients using the Fourier transform. % TODO: add reference to fourier transform in chapter 2
Once the coefficients are computed, the input and output sample pairs are split into train, test, and validation subsets. For the first type of input and output function pair, since the samples are independent of each other, a random sampling of the dataset without replacement is done to select the samples for each subset. For the second type of input and output function pairs, if there are multiple samples of functions as in the Burgers' equation dataset, the same process with random sampling is followed. On the other hand, if only one function sample is available, such as the WeatherBench 2 dataset, an issue that arises is the fact that the samples are dependent on one another. This is because a previous time step influences the next time step. This is a problem for generalizing the learned model, since random sampling would lead to the model learning information in the future of the testing subset \autocite{kapoorLeakageReproducibilityCrisis2023,kaufmanLeakageDataMining2012}. As such, the portioning of the dataset is done by dividing the sample into different sections of the function in time.

Finally, the data is scaled. This is done because of how support vector machines require scaling for inputs in order to perform well with certain hyperparameters such as the RBF kernel \autocite{ben-hurUsersGuideSupport2010}. For our case we use standard scaling based on the inputs of the training subset. This approach transforms the dataset by manipulating the distribution characteristics of the dataset \autocite{ahsanEffectDataScaling2021}. Specifically, the standard deviation \(\sigma \) and mean \(x_0\) of the dataset values \(x\) are processed such that the resulting values have a mean of 0 and standard deviation of 1. The function shown in \lccref{eq:standard_scaler} represents how each sample is processed with respect to the standard deviation \(\sigma \) and mean \(x_0\) of each feature.
\begin{equation}
  z(x;\sigma,x_0)=\frac{x-x_0}{\sigma} \label{eq:standard_scaler}
\end{equation}
The scaling is important for the RBF kernel specifically due to the fact that the kernel utilize a scale parameter. This parameter affects how scale of values influence the kernel. Another and perhaps more general benefit of scaling is the uniformity it enforces across features. This is useful because all feature weigh the outcome equally. In our use case, this equality is a reflection of what the data actually represents. Each feature which is a discretized value or its coefficient representation has equal value to any other feature. No point or coefficient is any more or less value compared to another point or coefficient.

The scaling is applied to input functions only because scaling of the outputs does not affect the performance of the model \autocite{ben-hurUsersGuideSupport2010}. To also prevent information leakage across training and testing sets, the mean and standard deviation of each feature is computed using the training subset only. Once the parameter values are obtained, all input function samples in the dataset are transformed into their scaled versions. This means that the distribution for the testing and validation sets may be outside the target standard deviation and mean. % TODO: add graphs and tables of the resulting preprocessed data

\subsection{Model Training}
\noindent Once the data has been preprocessed, the model is trained using pairs of training features and labels. The training phase is separated into four processes. First, the preprocessed input and output function representation need to be real numbers. This is because the LSSVR model was made to work with real numbers. Any complex values such as Fourier coefficients are represented as flattened pairs of the real and imaginary components of complex values. % TODO: add figure of flattened complex values

The training can proceed to solve \lccref{eq:lssvr_solution}. As the original LSSVR equation was made for regression of a single value of \(\vb{y} \), we constructed an extended the original equation in order to train multiple regression models to predict each coefficient in an output function sample. The assumption of this extension is that the inputs and model hyperparameters such as kernels and the regularization constant \(C \) are the same across individual regressors. Therefore, it follows that the solution vector and target vector can both be transformed into their matrix form with each column representing the individual regressor which results in \lccref{eq:lssvr_solution_vectorized}. This vectorized version is equal to \(m \) separate instances of \lccref{eq:lssvr_solution}. In essence, instead of a vector of scalar sample output values and a vector of model parameters, the extended equation consists of a matrix of rows of vector output values and a matrix of model parameters with each column representing the separate model for each output and row representing the Lagrange multipliers for each sample. The procedure to solve \lccref{eq:lssvr_solution_vectorized} adjusts \lccref{alg:lssvr_training} for the extra dimension spanning the multiple outputs of size \(m\).
\begin{equation} \label{eq:lssvr_solution_vectorized}
  \begin{bmatrix}
    0          & \vb{1}_{n}^{\intercal} \\
    \vb{1}_{n} & \Omega + \frac{I}{C}
  \end{bmatrix}
  \begin{bmatrix}
    b_0           & \cdots & b_m \\
    \vb{\alpha}_0 & \cdots & \vb{\alpha}_m\\
  \end{bmatrix}
  =
  \begin{bmatrix}
    0        & \cdots & 0 \\
    \vb{y}_0 & \cdots & \vb{y}_m \\
  \end{bmatrix}
\end{equation}

Second, as the training process of an LSSVR described in requires constructing the first matrix on the left-hand side and the matrix on the right-hand side, each component of the matrices themselves will also need to be constructed. The kernel matrix \(\Omega \) is first constructed by computing the kernel values between each sample input with every other sample input. If the training set has \(n \) samples, then the resulting kernel matrix would be of size \(n \) by \(n \).
% Assemble lssvr optimality equation matrices
Third, using the inputs \(\vb{X}\), outputs \(\vb{y}\), predetermined regularization constant \(C \), and the obtained kernel matrix \(\Omega \), \lccref{eq:lssvr_solution_vectorized} is assembled. Finally, the matrix of learned parameters \(\vb{\alpha}\) and \(\vb{b}\), which are the Lagrange multipliers and bias respectively, are solved for using a linear equation solver such as a matrix Moore-Penrose inverse or linear least squares solver.

% TODO: decide if hyperparameter selection is needed and explain why or why not. Maybe hyperparameter selection is done in a phase after the model evaluation with a decision between repeating model training with different hyperparameters or keeping the trained model.
Next, the selection of hyperparameters is done to optimize the model further. As previously mentioned, the hyperparameters are the regularization constant \(C \) and kernel functions including the kernel function parameters.

\subsection{Model Evaluation}
\noindent The fourth phase of the computational model is the evaluation of the learned model. This phase starts with formatting the inputs. If the inputs aren't scaled yet, then it is scaled using the scaler fitted on the training set. This is the case for new data such as new measurements or an analytical solution of the learned PDE\@. Once the inputs that is to be evaluated is scaled in the same way as the training inputs, the model can predict the corresponding outputs.

The procedure to compute the predicted outputs follows \lccref{alg:lssvr_prediction}. This leads to the second process which is computing the kernel matrix between the training input features \(\vb{X}\) and the evaluation input features \(\vb{U}\). The matrix is constructed as the kernel value between each evaluation sample feature and every training sample feature. For \(p \) evaluation samples and \(n \) training samples, this results in a kernel matrix \(\Omega \) with a shape of \(p \) rows and \(n \) columns.

In the third process, the constructed kernel matrix is then multiplied with the matrix of learned Lagrange multipliers \(\vb{\alpha}\). The multiplication is the matrix multiplication process. Then, the bias vector is added to each row to produce the final predicted outputs \(\vb{v}\). This process is represented by \lccref{eq:lssvr_prediction_vectorized}.
\begin{equation}
  \vb{v} = \Omega\vb{\alpha}+\vb{1}\vb{b} \label{eq:lssvr_prediction_vectorized}
\end{equation}

The fourth process is concerned with the fact that the predicted output \(\vb{v}\) is a matrix of real numbers. The LSSVR output needs to be formatted before it can be used in the proposed model. This is done by converting the outputs into the same format as the training labels. As we use the Fourier basis, the model output is converted back into a matrix of complex numbers using the inverse of the first process during training. Finally, these predicted Fourier basis coefficients can be used to evaluate the predicted functions themselves.

\section{Implementation of Computational Model}
\noindent This section discusses the implementation of modeling and approximation of PDEs using LSSVR\@. Using the computational model design in \lccref{sec:computational_model_design}, the computational model is implemented as a library using the Python programming language. The development process itself is based on the iterative development model as mentioned in \lccref{sec:development method}. In this section, the output iterative processes are consolidated and explained together.

\subsection{Analysis}
\noindent The aim of any program that is developed in this study is to model the relationship between functions defined by a partial differential equation or other operators and governing equations. Since the potential subject of modeling can be wide-ranging, the software product that will be developed is a library. This is done so that the tools and proposed model that is developed will be able to be used with a variety of PDEs. With this in mind, the software must also be performant and compatible with the larger machine learning and scientific computing community.

To demonstrate the use and capability of the software, three case studies are chosen to represent the variety of PDEs. The first case study is the antiderivative equation. This simple case is chosen as a proof of concept to show that the proposed model works in the most simple case. The second case study, which is the Burgers' equation, adds a level of complexity because of the nonlinearity involved with the solution function. The third case study, which is the ERA5 weather dataset, was chosen to show how the model performs on data with real world observations incorporated into it. This dataset also presents a challenge because of the uncertainties involved with weather simulation \autocite{herreraReviewCurrentFuture2017}. These datasets are discussed in \lccrefs{sec:data_generation,sec:data_retrieval}.

In addition, the software product is developed within certain limitations. The limitations are:
\begin{enumerate}
  \item The operating and implementation language of the library is Python.
  \item The library is to be used in user code
  \item The library depends on other libraries including the following core dependencies Pytorch, Numpy, Xarray, Zarr, Pandas, and tqdm.
\end{enumerate}

\subsection{Design}
\noindent In this subsection, the architectural design of the software product is explained. The architecture consists of modules with similar concerns. This was chosen because of the intuition built by the use of other libraries with a similar architecture. The broad aim of modeling PDEs with LSSVR and basis functions coefficients can be separated into smaller concerns of data, model, basis functions, and utilities.

\subsection{Implementation}

\subsection{Testing}
